Walling up Backdoors in Intrusion Detection Systems

### 2019-10-15 paper/paper.tex
Add more info to figure
Adapt figures

\subsubsection{Fine-Tuning}
%\todo{Max: It said pruning before but should be tuning, right?}
%AH. I guess both should work
\begin{figure}[b]
%\includegraphics[width=\columnwidth]{figures/finetuning_2015.pdf}
\includegraphics[width=\columnwidth]{figures/finetuning_2017.pdf}
\caption{Fine-tuning of the \gls{mui} for \unsw{}.}
\label{fig:finetuning}
\end{figure}
In addition to pruning, we tried to use fine-tuning to remove the backdoor from the \gls{mlp}. % classifier.
%The use of
Fine-tuning exclusively makes  sense if both the computational effort and the required training set size for fine-tuning are substantially lower than for the original training procedure.

@@

\autoref{fig:pruningExample} shows an example of variant (3) of pruning applied to a tree
\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/prune_CAIA_backdoor_15/prune_oh_d.pdf}
\caption{Pruning an \gls{rf} for \unsw{}.}
\label{fig:performancePruningRF}
\end{figure}
%\todo{Max: Which pruning algorithm actually?}
and \autoref{fig:performancePruningRF} shows the resulting accuracy for pruning according to variant (3) for the \unsw{} dataset. With sufficient leaves being pruned, the accuracy of the backdoor approaches zero. The accuracy for the regular data does not decrease significantly. It might even increase by reducing overfitting. With 90\% of leaves pruned, accuracy is still well above 99\%. Even with a very small validation set of just 1\% of its original size, the pruning still works as expected.

>>>>

\subsubsection{Fine-Tuning}
%\todo{Max: It said pruning before but should be tuning, right?}
%AH. I guess both should work
\begin{figure}[b]
%\includegraphics[width=\columnwidth]{figures/finetuning_2015.pdf}
\includegraphics[width=\columnwidth]{figures/finetuning_2017.pdf}
\caption{Fine-tuning of the \gls{mui} for \unsw{}: While fine-tuning finally lowers backdoor accuracy a little bit, it takes more training epochs than training the original model.}
\label{fig:finetuning}
\end{figure}
In addition to pruning, we tried to use fine-tuning to remove the backdoor from the \gls{mlp}. % classifier.
%The use of
Fine-tuning exclusively makes  sense if both the computational effort and the required training set size for fine-tuning are substantially lower than for the original training procedure.

@@

\autoref{fig:pruningExample} shows an example of variant (3) of pruning applied to a tree
\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/prune_CAIA_backdoor_15/prune_oh_d.pdf}
\caption{Pruning an \gls{rf} for \unsw{}. The smaller the dashes, the smaller the validation dataset. The validation set size ranges from 1\% to 100\% of its original size.}
\label{fig:performancePruningRF}
\end{figure}
%\todo{Max: Which pruning algorithm actually?}
and \autoref{fig:performancePruningRF} shows the resulting accuracy for pruning according to variant (3) for the \unsw{} dataset. With sufficient leaves being pruned, the accuracy of the backdoor approaches zero. The accuracy for the regular data does not decrease significantly. It might even increase by reducing overfitting. With 90\% of leaves pruned, accuracy is still well above 99\%. Even with a very small validation set of just 1\% of its original size, the pruning still works as expected.
